\documentclass[a4paper,12pt]{report}
\usepackage{setspace} % For controlling line spacing
\usepackage{amsmath, amsthm, amssymb} % For mathematical symbols and environments
\usepackage{graphicx} % For including figures
\usepackage{hyperref} % For clickable references
\usepackage{cite} % For citation management

% Theorem-like environments
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{remark}{Remark}[section]

\begin{document}
\onehalfspacing


\setlength{\parskip}{\baselineskip}


\begin{thebibliography}{9} % The number '9' is just a width for numbering, adjust based on your needs

\bibitem{zebra2023} 
Zebra. (Jan. 2023). Drowsy Driving Statistics. [Online]. Available:  
\texttt{https://www.thezebra.com/resources/research/drowsy-driving-statistics}

\bibitem{madni2024} 
H. A. Madni, A. Raza, R. Sehar, N. Thalji, and L. Abualigah,  
"Novel Transfer Learning Approach for Driver Drowsiness Detection Using Eye Movement Behavior,"  
\textit{IEEE Access}, vol. 12, pp. 64765-64778, 2024, doi: 10.1109/ACCESS.2024.3392640.

\bibitem{ran2023} 
X. Ran, S. He, and R. Li,  
"Research on Fatigued-Driving Detection Method by Integrating Lightweight YOLOv5s and Facial 3D Keypoints,"  
\textit{Sensors}, vol. 23, p. 8267, 2023.

\bibitem{guo_markoni} 
J.-M. Guo and H. Markoni,  
"Driver drowsiness detection using hybrid convolutional neural network and long short-term memory."

\bibitem{kolus2024} 
A. Kolus,  
"A Systematic Review on Driver Drowsiness Detection Using Eye Activity Measures,"  
\textit{IEEE Access}, vol. 12, pp. 97969-97993, 2024, doi: 10.1109/ACCESS.2024.3424654.

\bibitem{ramzan2024} 
M. Ramzan, A. Abid, M. Fayyaz, T. J. Alahmadi, H. Nobanee, and A. Rehman,  
"A Novel Hybrid Approach for Driver Drowsiness Detection using a Custom Deep Learning Model,"  
\textit{IEEE Access}, doi: 10.1109/ACCESS.2024.3438617, 2024.

\bibitem{venkatsewarulu_reddy} 
M. Venkatsewarulu and V. R. Reddy CH,  
"DrowsyDetectNet: Driver Drowsiness Detection Using Lightweight CNN With Limited Training Data."

\bibitem{ruiz2018} 
N. Ruiz, E. Chong, and J. M. Rehg,  
"Fine-Grained Head Pose Estimation Without Keypoints,"  
\textit{arXiv preprint arXiv:1710.00925v5}, 2018.

\bibitem{ye2023} 
M. Ye, W. Zhang, P. Cao, and K. Liu,  
"Driver Fatigue Detection Based on Residual Channel Attention Network and Head Pose Estimation."

\bibitem{krizhevsky2012imagenet}
Krizhevsky, A., Sutskever, I., \& Hinton, G. E. (2012). ImageNet classification with deep convolutional neural networks. Advances in neural information processing systems, 25.

\bibitem{simonyan2014very}
Simonyan, K., \& Zisserman, A. (2014). Very deep convolutional networks for large-scale image recognition. arXiv preprint arXiv:1409.1556.

\bibitem{he2016deep}
He, K., Zhang, X., Ren, S., \& Sun, J. (2016). Deep residual learning for image recognition. In Proceedings of the IEEE conference on computer vision and pattern recognition (pp. 770-778).


\end{thebibliography}

\end{document}